Computing Entropies With Nested Sampling

### 2017-05-19 paper/ms.tex
Bit of appendix writing
slight amount of work
Sentence at the end

The entropy of the precisional question is built up from
$Q$ terms. The extra entropy from adding the interval
$[x_0, x_0 + L]$ and removing the overlap $[x_0, x_0 + L - h]$, for small $h$, is
\begin{align}
\delta H &= Q(x_0, L) - Q(x_0, L - h)\\
         &= h\frac{\partial Q}{\partial L} \\
         &= -h\left[1 + \log P(x_0, L)\right]f(x_0 + L).
\end{align}
Therefore, the overall entropy is
\begin{align}
H &=
      -\int_{-\infty}^\infty
        \left[1 + \log P(x-L, L)\right]f(x)
      \, dx
\end{align}
which is connected to the expected value of the log-probability.

>>>>

The entropy of the precisional question is built up from
$Q$ terms. The extra entropy from adding the interval
$[x_0, x_0 + L]$ and removing the overlap $[x_0, x_0 + L - h]$, for small $h$, is
\begin{align}
\delta H &= Q(x_0, L) - Q(x_0, L - h)\\
         &= h\frac{\partial Q}{\partial L} \\
         &= -h\left[1 + \log P(x_0, L)\right]f(x_0 + L).
\end{align}
Therefore, the overall entropy is
\begin{align}
H &= -\int_{-\infty}^\infty
        \left[1 + \log P(x-L, L)\right]f(x)
      \, dx \\
  &= -\int_{-\infty}^\infty
        \left(1 + \log\left[F(x) - F(x-L)\right]\right)f(x)
      \, dx.
\end{align}
Interestingly, calculating the log-probability of an interval
to the right of $x$ gives an equivalent result:
\begin{align}
H' &=  -\int_{-\infty}^\infty
        \left(1 + \log\left[F(x+L) - F(x)\right]\right)f(x)
      \, dx \\
   &= H.
\end{align}
This is not quite the same as the expected log-probability calculated by
the version of the algorithm proposed in this paper (when the tolerance is not
small).
